### 2014-08-05 paper/paper.tex
Changed the instructions to reflect the change in repository name
Fixed the docs to reflex the new brach

\begin{enumerate}
    \item \textbf{Download Source} - The source code is hosted on github.com
        and can be viewed
        \href{https://github.com/hockeybuggy/semantic\_eval}{here}. To download a zip
        file and open it:

\begin{Verbatim}[fontsize=\footnotesize]
wget https://github.com/hockeybuggy/semantic_eval/archive/master.zip
unzip master.zip
cd master
\end{Verbatim}

>>>>

    \item \textbf{Download Source} - The source code is hosted on github.com
        and can be viewed there
        \footnote{https://github.com/hockeybuggy/twitter-sentiment}. To download a
        zip file and open it:

\begin{Verbatim}[fontsize=\footnotesize]
wget https://github.com/hockeybuggy/twitter-sentiment/archive/dist.zip -O tsent.zip
unzip tsent.zip
cd tsent
\end{Verbatim}
